Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-11 extrinsic_type_inference_paper/paper.tex
add some notes on induction

>>>>

\TODO{inductive reasoning, in the general sense, consists of learning sufficient conditions P that enable deriving Q }

\TODO{reasoning by cases consists of deriving P implies Q 
by ensuresing P' implies Q for every P' that implie P
}

\TODO{mathematical induction is a particular form of reasoning by cases
where P is recursively defines, so P' resembles it, and for any P' that resembles P,
we can assume that P' -> Q', where Q' resembles Q.
}
